Position: Stop Making Unscientific AGI Performance Claims

### 2024-05-31 arxiv.tex
updated arxiv pre-print version

\renewcommand{\shorttitle}{Position Paper: Against Spurious Sparks---Dovelating Inflated AI Claims}

@@

\title{Position Paper:\\Against Spurious Sparks---Dovelating Inflated AI Claims \raisebox{-6pt}{\includegraphics[scale=0.09]{dove_1f54a-fe0f.png}}}

@@

@@

>>>>

\renewcommand{\shorttitle}{Position: Stop Making Unscientific AGI Performance Claims}

@@

\title{Position: Stop Making Unscientific AGI Performance Claims}

@@

\twocolumn

@@

\section*{Impact Statement}
This work was written out of concern that work easily recognized as `impactful' in current AI research and development, can also easily be over- and misinterpreted. As such, in the current climate of high market demand for AI innovations, we see risks of too-eager adoption in real-world applications, which may have serious societal impact. Thus, in this work we emphasize that an academic's impact also is in being able to thoroughly question made claims, and being explicitly aware of one's own biases. While the AI publishing landscape has to our feeling transformed too much into a noisy race to get exciting results in fast, we hope the research community can create more room for this type of deeper questioning.

\section*{Acknowledgements}

Some of the members of TU Delft were partially funded by ICAI AI for Fintech Research, an ING---TU Delft collaboration.

\section*{CRediT Author Statement}
Following the CRediT Contributor Roles Taxonomy, we list author contributions in descending order of degree of contribution: \textbf{Conceptualization} PA, AD, AB, CL; \textbf{Data curation} PA; \textbf{Formal analysis} PA; \textbf{Funding acquisition} CL; \textbf{Investigation} PA; \textbf{Literature review} AD, AB, CL; \textbf{Methodology} PA, CL; \textbf{Project administration} PA, AD, AB; \textbf{Software} PA; \textbf{Supervision} CL; \textbf{Visualization} PA; \textbf{Writing - original draft} PA, AD, AB; \textbf{Writing - review and editing} PA, AD, AB, CL.

### 2024-05-31 body.tex
updated arxiv pre-print version

\begin{itemize}
 \item \textbf{Acknowledgement of human bias}: researchers should be mindful of, and explicit about, risks of human bias and anthropomorphization in interpreting results, which both can be done as part of the results discussion, but also in a dedicated `limitations' section.
 \item \textbf{Stronger testing}: researchers should refrain from drawing premature conclusions about AGI, unless these are based on strong hypothesis tests.
 \item \textbf{Epistemologically robust standards}: we call for more precise definitions of terms like ‘intelligence’ and ‘AGI’, and publicly accountable and collaborative iterations over how we will measure them, with explicit room for independent reviewing and external auditing by the broader community.
\end{itemize}
%firstly, researchers should consider acknowledging our tendency to anthropomorphize either in a dedicated ‘limitations’ section or when discussing results (\textit{acknowledgment}); secondly, researchers should refrain from drawing premature conclusions about AGI, unless these conclusions are based on strong hypothesis tests (\textit{stronger testing}); thirdly, we call for more precise definitions of terms like ‘intelligence’ and ‘AGI’, and iterations over how we will measure them (\textit{epistemologically robust standards}).

@@

\section*{Impact Statement}
This work was written out of concern that work easily recognized as `impactful' in current AI research and development, can also easily be over- and misinterpreted. As such, in the current climate of high market demand for AI innovations, we see risks of too-eager adoption in real-world applications, which may have serious societal impact. Thus, in this work we emphasize that an academic's impact also is in being able to thoroughly question made claims, and being explicitly aware of one's own biases. While the AI publishing landscape has to our feeling transformed too much into a noisy race to get exciting results in fast, we hope the research community can create more room for this type of deeper questioning.

>>>>

\begin{enumerate}
 \item (\textit{Acknowledgement of Human Bias}) Researchers should be mindful of, and explicit about, risks of human bias and anthropomorphization in interpreting results, which both can be done as part of the results discussion, but also in a dedicated `limitations' section.
 \item (\textit{Stronger Testing}) Researchers should refrain from drawing premature conclusions about AGI, unless these are based on strong hypothesis tests.
 \item (\textit{Epistemologically Robust Standards}) We call for more precise definitions of terms like ‘intelligence’ and ‘AGI’, and publicly accountable and collaborative iterations over how we will measure them, with explicit room for independent reviewing and external auditing by the broader community.
\end{enumerate}
%firstly, researchers should consider acknowledging our tendency to anthropomorphize either in a dedicated ‘limitations’ section or when discussing results (\textit{acknowledgment}); secondly, researchers should refrain from drawing premature conclusions about AGI, unless these conclusions are based on strong hypothesis tests (\textit{stronger testing}); thirdly, we call for more precise definitions of terms like ‘intelligence’ and ‘AGI’, and iterations over how we will measure them (\textit{epistemologically robust standards}).

@@

### 2024-05-31 main.tex
updated arxiv pre-print version

@@

\section*{CRediT Author Statement}
Following the CRediT Contributor Roles Taxonomy, we list author contributions in descending order of degree of contribution: \textbf{Conceptualization} PA, AD, AB, CL; \textbf{Data curation} PA; \textbf{Formal analysis} PA; \textbf{Funding acquisition} CL; \textbf{Investigation} PA; \textbf{Literature review} AD, AB, CL; \textbf{Methodology} PA, CL; \textbf{Project administration} PA, AD, AB; \textbf{Software} PA; \textbf{Supervision} CL; \textbf{Visualization} PA; \textbf{Writing - original draft} PA, AD, AB; \textbf{Writing - review and editing} PA, AD, AB, CL.
\bibliography{biblio}
\bibliographystyle{icml2024}

>>>>

\section*{Impact Statement}
This work was written out of concern that work easily recognized as `impactful' in current AI research and development, can also easily be over- and misinterpreted. As such, in the current climate of high market demand for AI innovations, we see risks of too-eager adoption in real-world applications, which may have serious societal impact. Thus, in this work we emphasize that an academic's impact also is in being able to thoroughly question made claims, and being explicitly aware of one's own biases. While the AI publishing landscape has to our feeling transformed too much into a noisy race to get exciting results in fast, we hope the research community can create more room for this type of deeper questioning.

@@

\section*{CRediT Author Statement}
Following the CRediT Contributor Roles Taxonomy, we list author contributions in descending order of degree of contribution: \textbf{Conceptualization} PA, AD, AB, CL; \textbf{Data curation} PA; \textbf{Formal analysis} PA; \textbf{Funding acquisition} CL; \textbf{Investigation} PA; \textbf{Literature review} AD, AB, CL; \textbf{Methodology} PA, CL; \textbf{Project administration} PA, AD, AB; \textbf{Software} PA; \textbf{Supervision} CL; \textbf{Visualization} PA; \textbf{Writing - original draft} PA, AD, AB; \textbf{Writing - review and editing} PA, AD, AB, CL.

\bibliography{biblio}
\bibliographystyle{icml2024}
